---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# srilankamotif

<!-- badges: start -->
<!-- badges: end -->

This package is developed to generate Sri Lankan-inspired artistic motifs using R through mathematical and geometric constructions. Beyond its visual outputs, the package serves an educational purpose by demonstrating how mathematics can be translated into art through coding, helping users strengthen their programming skills, particularly in data visualization and functional programming in R, while engaging in creative exploration.


## Installation

You can install the development version of srilankamotif from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("thiyangt/srilankamotif")
```

```{r}
library(srilankamotif)
library(ggplot2)
```


## Example

## Inspired by Lotus


```{r example}
library(srilankamotif)
## basic example code
generate_flower()
```

## Inspired by Binara (බිනර) Mala 

```{r}
draw_dual_2flowers()
```

```{r}
generate_binara_3flower()
```

# Inspired by Arimbuwa

```{r}
generate_arimbuwa()
```

## Inspired by Gal Binduwa (ගල් බින්දු)

```{r}
generate_galbinduwa()
```

## References

[Traditional Sinhala Degins](https://upload.wikimedia.org/wikipedia/commons/e/e9/%E0%B6%B4%E0%B7%90%E0%B6%BB%E0%B6%AB%E0%B7%92_%E0%B7%83%E0%B7%92%E0%B6%82%E0%B7%84%E0%B6%BD_%E0%B6%B8%E0%B7%9D%E0%B7%83%E0%B7%8A%E0%B6%AD%E0%B6%BB_old_sinhala_designs.jpg)
