---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# srilankamotif

<!-- badges: start -->
<!-- badges: end -->

This package is developed to generate Sri Lankan-inspired artistic motifs using R through mathematical and geometric constructions. Beyond its visual outputs, the package serves an educational purpose by demonstrating how mathematics can be translated into art through coding, helping users strengthen their programming skills, particularly in data visualization and functional programming in R, while engaging in creative exploration.

This project lies at the intersection of Art, Mathematics, and Programming. Art provides the creative inspiration through traditional Sri Lankan motifs and aesthetic design principles. Mathematics contributes the underlying geometric structures, symmetry, repetition, and pattern formation that characterize these motifs. Programming serves as the medium that transforms artistic ideas and mathematical concepts into reproducible digital designs through algorithms and code.

By combining these three disciplines, the project explores how cultural heritage can be represented computationally. Traditional decorative patterns are translated into mathematical rules and implemented using programming, enabling the creation, visualization, and exploration of Sri Lankan motifs in a systematic and reproducible manner. The result is a fusion of creativity, logic, and technology, demonstrating how artistic expression can emerge from mathematical thinking and computational methods.

Figure 1. This project lies at the intersection of Art, Mathematics, and Programming.

```{r echo=FALSE, fig.cap="Figure 1: Intersection of Art, Mathematics, and Programming"}
knitr::include_graphics(
  "https://raw.githubusercontent.com/thiyangt/srilankamotif/main/project.png"
)
```

## Installation

You can install the development version of srilankamotif from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("thiyangt/srilankamotif")
```

```{r}
library(srilankamotif)
library(ggplot2)
```


## Example

## Inspired by Lotus


```{r example}
library(srilankamotif)
## basic example code
generate_flower()
```

## Inspired by Binara (බිනර) Mala 

```{r}
draw_dual_2flowers()
```

```{r}
generate_binara_3flower()
```

# Inspired by Arimbuwa

```{r}
generate_arimbuwa()
```

## Inspired by Gal Binduwa (ගල් බින්දු)

```{r}
generate_galbinduwa()
```

## Traditional Sinhala Designs

Clear [here](https://upload.wikimedia.org/wikipedia/commons/e/e9/%E0%B6%B4%E0%B7%90%E0%B6%BB%E0%B6%AB%E0%B7%92_%E0%B7%83%E0%B7%92%E0%B6%82%E0%B7%84%E0%B6%BD_%E0%B6%B8%E0%B7%9D%E0%B7%83%E0%B7%8A%E0%B6%AD%E0%B6%BB_old_sinhala_designs.jpg) to view traditional sinhala designs.

